---
title: "Classification"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mlr)
```

## Introduction

Provide a thoughtful and insightful analysis of a classification problem.
First get familiar with the data.

```{r data}
library(nycflights13)
library(dplyr)

# Predicting whether a flight is delayed from weather data.

# Join the weather data to destination and origin
flights_weather = flights %>%
  inner_join(weather) %>%
  select(-time_hour)
# Relevant features:
flights_weather %>%
  select(one_of(c("hour", "origin", "dest", "dep_delay", 
    "temp", "dewp", "humid", "wind_dir",
    "wind_speed", "wind_gust", "precip", "pressure",
    "visib"))) %>% 
      mutate(is_delayed = dep_delay > 5) %>%
  select(-dep_delay)

# Carefully select features you want to use! 

```

## Insightfull Analysis

In this chapter you are supposed to give an insight to the data.
What are the characterisitcs of each class and which factors contribute mainly to the classification

## Predictive Analysis

In this chapter the goal is to find the best performing model.
Optimize the Accuracy `acc` using tuning methods or benchmarking functions of mlr.
