---
title: "Imbalanced Classification"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  cache = TRUE
)
library(mlr)
```

## Introduction

Provide a thoughtful and insightful analysis of the machine learning problem you chose.
This includes providing an understanding of the features a proper validation of the model that gives an reliable estimate of the prediction performance.

## Reading the dataset

Read the dataset. You might want to downsample it for a faster analysis and only later use the full dataset.

```{r}
# just an example
library(data.table)
data = fread("...")
```

## Exploration

Get in touch with the features of the dataset.

* Does the data have missing values? 
* Categorical features?
* Features that need preprocessing?

In this chapter you are also supposed to give an insight to the data.

## Benchmark

Benchmark different learners or tune the hyperparemeters to obtain a good predictive performance.

## Interpret Results

Can you use the obtained model to get deeper insights about the relationship bettween the features and the label?