---
title: "Advanced - Wrappers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mlr)
```

## Introduction

Can you think of any analysis steps, such as parts of preprocessing that involve setting additional
parameters, which (optimally) can be tuned?
As an example look at preprocessing wrappers, such as `makePreprocWrapperCaret` and 
`makeImputeWrapper()`

Some examples:
* Feature hashing
* Binning numeric features
* Smoothing functional observations

Provide a guide on how to create and tune such (custom) wrappers and apply it to a suitable problem.
Some ideas for application datasets:
https://archive.ics.uci.edu/ml/datasets/semeion+handwritten+digit
https://archive.ics.uci.edu/ml/datasets/Amazon+Commerce+reviews+set
Kaggle: Deaths in the United States

## Creating a wrapper

Show how to create the wrapper and explain the neccessary steps.
```{r}
wrp = makePreprocWrapper(...)
```


## Applying the wrapper

Showcase how the wrapper works in a simple example.


## Tuning the learner and the wrapper.

Showcase how wrappers and learners can be tuned jointly in a simple example.
